Are mental properties supervenient on brain properties?

### 2011-07-26 nature_sci_rep/submission2/supervenience.tex
ready for cep redlines

If minds statistically supervene on brains, $\MsB$, then if two minds differ, there must be some brain-based difference to account for the mental difference.  This means that there exists a deterministic function mapping each brain to its supervening mind, $g: \mB \mapsto \mM$. One could therefore, in principle, construct this function. When the space of all possible minds is finite; that is, $|\mM| < \infty$, $g$ is called a \emph{classifier}.  
% Let $\mh{m}$ denote the output of a classifier, $g(b)=\mh{m}$.  
Define misclassification rate, the probability that $g$ misclassifies $b$ under distribution $F=F_{MB}$,  as
\begin{align}
L_{F}(g) = \PP[g(B) \neq M] = \frac{1}{|\mc{M} \times \mc{B}|} \sum_{(m,b) \in \mc{M} \times \mc{B}} \II\{g(b) \neq m\} \PP[B=b, M=m]	
\end{align}
where $\II$ denotes the indicator function taking value unity whenever its argument is true, and zero otherwise.  The Bayes optimal classifier $g^*$ minimizes $L_{F}(g)$ over all classifiers, that is:	
$g^* = \argmin_{g} L_{F}(g)$.
The \emph{Bayes error}, or Bayes risk, $L^*=L_{F}(g^*)$, is the minimum possible misclassification rate.

@@

\subsection*{The intractability of testing for statistical supervenience} % (fold)
\label{sub:subsection_name}

@@

Although the above theorem is of potential theoretical interest, the argument relies on knowing the typically unavailable $L^*$, rendering it useless pragmatically.  However,  $g^*$ could be estimated from data, and its estimate could be utilized to conduct the following statistical test of supervenience:
% Let $g_n$ be a classifier induced from some training data, $\mc{T}_n$, 
\begin{align*} 
	H_0:& L^* > 0 \\
	H_A:& L^*=0
\end{align*}
A statistical test proceeds by calculating a test statistic and a critical value $c_\alpha$.  We reject if the test statistic is more extreme than the critical value, or equivalently, if the $p$-value is less than $\alpha$.   The $p$-value, the probability of rejecting a true null hypothesis, is a function of the distribution of the test statistic.

Let $g_n$ be a classifier induced by the data, $g_n:\mB \times (\mc{M} \times \mc{B})^n \mapsto \mM$.   Assume that training data $\mc{T}_n=\{(M_{1},B_{1}), \ldots, (M_{n},B_{n})\}$ are each sampled identically and independently (iid) from the true (but unknown) joint distribution, $F_{MB}$.  The misclassification rate of a classifier will therefore be a random variable. The expected misclassification rate is given by 
\begin{align}
\EE[L_F(g_n)]=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m].
\end{align}
Because calculating the expected misclassification rate requires a sum over all possible mind/brain property pairs, calculating $\EE[L_F(g_n)]$ will often be intractable in practice.  Instead, expected misclassification rate is approximated by ``hold-out'' error.  Let $\mc{H}_{n'}=\{(M_{n+1},B_{n+1}), \ldots, (M_{n+n'},B_{n+n'})\}$ be a set of $n'$ hold-out samples, each sampled iid from $F_{MB}$.  The hold-out approximation to misclassification rate is given by
\begin{align}
\hL^{n'}_{F}(g_{n}) = \sum_{(m,b) \in \mc{H}_{n'}}\II \{g_{n}(b; \mc{T}_{n})\neq m] \PP[B=b,M=m].	
\end{align}
Under the above assumptions, $\hL^{n'}_F(g_n)$ can be used as a surrogate for $L^*$.  By definition of $g^*$, we expect $\hL^{n'}_F(g_n) \geq g^*$ for any $g_n$ and all $n$.   We therefore let $\mh{n}= \lfloor n' \hL^{n'}_{F}(g_n) \rfloor$ be the test statistic, where $\lfloor \cdot \rfloor$ is the floor operator.  The distribution of $\mh{n}$ is available under the least favorable distribution of the alternate hypothesis.  Specifically,  the $p$-value is given by the binomial cumulative distribution function, $\mathbb{B}(\mh{n}; n', p_{H_A})= \sum_{k \in [\mh{n}]}$Binomial$(k; n'; p_{H_A})$, where $p_{H_A}$ is Bernoulli probability under least favorable distribution of the alternate hypothesis and $[\mh{n}]=\{1,\ldots, \mh{n}\}$.  In this simple alternate hypothesis, $p_{H_A}=0$. Because Binomial$(k; n', 0)=1$ for all $n'$, the $p$-value is always equal to unity.    Thus, we can \emph{never} reject the above null hypothesis, no matter how much data we obtain.

\subsection*{$\eps$-supervenience admits hypothesis testing} % (fold)
\label{sub:hypothesis_testing}

We therefore consider a relaxed notion of supervenience:
\begin{defi}
\label{def2}
Given $\varepsilon > 0$, $\mM$ is said to $\varepsilon$-\textit{supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\MeB$, if and only if $L_{F}(g^*) < \varepsilon$.
\end{defi}
\noindent Given this relaxation, consider the problem of testing for $\eps$-supervenience:
\begin{align*}
	H_0^{\eps}: L^* \geq \eps \\
	H_A^{\eps}: L^* < \eps
\end{align*}
The $p$-value of the above composite alternate hypothesis is given by the binomial distribution under the least favorable distribution, $\mathbb{B}(\mh{n}; n', p_{H_A}=\eps)<1$.  We therefore reject whenever this $p$-value is less than $\alpha$; rejection implies that we are $100(1-\alpha$)\% confident that $\MeB$.   The definition of $\eps$-supervenience therefore admits, for the first time to our knowledge, a viable statistical test of supervenience, given a specified $\eps$ and $\alpha$.

\subsection*{A \emph{Gedankenexperiment} demonstrating an ideal test} % (fold)
\label{sub:uc}

Ideally, as $n$ increases, the probability of both a Type I error (rejection of a true null hypothesis) and a Type II error (failure to reject a false null hypothesis) goes to zero.

@@

The $p$-value 
(probability of a type I error)
of the test statistic for any classifier $g_n$ converges to zero, because $\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n))) \conv 0$ as $n,n' \conv \infty$. The power of the test (probability of not making a type II error), however, only converges to unity under certain conditions.  Specifically, let a  \emph{consistent} classifier be any classifier with expected misclassification rate converging to the Bayes optimal limit; that is, $\EE[L_{F}(g_n)] \conv L_{F}(g^*)$ as $n\conv \infty$. The power of the test can be written as: $\PP[\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n)) < \mathbb{B}(\mh{n}; n', \eps)]$.  As $n,n' \conv \infty$, $\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n)) \conv \mathbb{B}(\mh{n}; n', L^*)$.  And if $L^* < \eps$, then $\mathbb{B}(\mh{n}; n', L^*) < \mathbb{B}(\mh{n}; n', \eps)$.  So, the probability of a Type II error also goes to zero as $n,n' \conv \infty$.

@@

Below, we show that under a very general mind-brain model, one can construct a consistent classifier whose power approaches unity with sufficient data.

@@

\begin{thex}
Let the physical property under consideration be brain connectivity structure, so $b$ is a brain-graph (``connectome'') with vertices representing neurons (or neuroanatomical regions) and edges representing synapses (or white matter tracts). Further let $\mB$, the brain observation space, be the collection of all graphs on a finite number of vertices, and $\mc{M}$, the mental property observation space, be finite. Now, imagine collecting very large amounts of very accurate exchangeable  brain-graph data and the associated mental property indicators. A $k_n$-nearest neighbor classifier using an isomorphism-matching Frobenius norm is universally consistent (see Appendix 2 for proof sketch). Therefore, %Theorem \ref{thm1} applies and 
the existence of a universally consistent classifier guarantees that eventually (in $n,n'$) we will be able to conclude $\MeB$ for this mind-brain property pair, if indeed $\varepsilon$-supervenience holds. This logic holds for directed graphs or multigraphs or hypergraphs with discrete edge weights and vertex attributes. Furthermore, Appendix 2 also extends the proof to deal with other matrix norms (which might speed up convergence), and the regression scenario, where $|\mM|$ is infinite.  
\end{thex}

@@

We have introduced the notion of $\eps$-supervenience, which states that the Bayes optimal misclassification rate for any mind-brain property pair is less than $\eps$.  Furthermore, when we restrict the space of minds and brains to the setting of \emph{Gedankenexperiment}  1, we have shown that $k_n$-NN classifiers are universally consistent, such that one can derive a hypothesis test, with confidence level $\alpha$, that is guaranteed to converge to the Bayes optimal misclassification rate, given sufficient data, no matter the true (but unknown) distribution of mind-brain pair properties.

@@

Thus, given measurement of mental and brain properties that we believe reflect the properties of interest, and a sufficient amount data satisfying the exchangeability assumption, a rejection entails that we are $100(1-a)\%$ confident that the mental property under investigation does not supervene on the brain property under investigation.  Unfortunately, failure to reject is more ambiguous. $\eps-$supervenience tests can therefore be thought of as constraining the space of possible brain properties upon which a mental property supervenes.  Determining that a mental property does not supervene on \emph{any} brain property is beyond the capacities of this formalism.

Interestingly, much of contemporary research in neuroscience and cognitive science could be cast as mind-brain supervenience investigations.  Specifically, any investigation that aims to ``explain'' some behavioral or psychological phenomenon by reference to neural (or other brain) activity or structure, could be thought of as mind-brain supervenience investigations.  Thus, the proposed $\eps$-supervenience framework is perhaps a useful unifying perspective for these fields.  Perhaps this is especially true in light of the advent of ``connectomics'' \cite{SpornsKotter05,Hagmann05}, a field devoted to estimating whole organism brain-graphs, and relating them to function.  Testing supervenience of various mental properties on these brain-graphs will likely therefore become increasingly compelling; so the framework developed herein could be fundamental to these investigations.  Note that these connectomics investigations might lack any dynamics; rather, they effectively assume that structure determines the relevant dynamics.  Assuming that dynamics are a function of either vertex or edge attributes, whether any particular mental property is supervenient to ``only'' connectivity structure, or also some attributes, is merely another $\eps$-supervenience hypothesis. Appendix 3 presents an illustrative simulated example using the only currently known connectome---that of a Caenorhabditis elegans---demonstrating that $\eps$-supervenience can be rejected at some critical value $c_\alpha$ with only a reasonably small number of samples. Similar supervenience tests on larger animals will require either higher-throughput imaging modalities \cite{HayworthLichtman06, Bock2011} or more coarse brain-graphs \cite{PalmAmunts10,Johansen-Berg2009}, or both.

@@

In conclusion, this \emph{Gedankenexperiment}, together with (i) the formal definition of $\varepsilon$-supervenience as a constraint on distributions, (ii) the brain-graph model, and (iii) the universal consistency proof on graphs, is the first demonstration (to our knowledge) that empirically investigating supervenience is at least theoretically possible. The above discussion suggests that many previously conducted investigations either assume supervenience, or try to test it.  Further, new technologies facilitate testing supervenience of mental properties on brain-graphs more easily.

\section*{Methods}
\label{sec:methods}
% \subsection*{Supervenience} % (fold)
% \label{sec:preliminaries}

>>>>

If minds statistically supervene on brains, $\MsB$, then if two minds differ, there must be some brain-based difference to account for the mental difference.  This means that there exists a deterministic function mapping each brain to its supervening mind, $g: \mB \mapsto \mM$. One could therefore, in principle, construct this function. When the space of all possible minds is finite; that is, $|\mM| < \infty$, $g$ is called a \emph{classifier}.  
% Let $\mh{m}$ denote the output of a classifier, $g(b)=\mh{m}$.  
Define misclassification rate, the probability that $g$ misclassifies $b$ under distribution $F=F_{MB}$,  as
\begin{align}
L_{F}(g) = \PP[g(B) \neq M] =  \sum_{(m,b) \in \mc{M} \times \mc{B}} \II\{g(b) \neq m\} \PP[B=b, M=m]	
\end{align}
where $\II$ denotes the indicator function taking value unity whenever its argument is true, and zero otherwise.  The Bayes optimal classifier $g^*$ minimizes $L_{F}(g)$ over all classifiers, that is:	
$g^* = \argmin_{g} L_{F}(g)$.
The \emph{Bayes error}, or Bayes risk, $L^*=L_{F}(g^*)$, is the minimum possible misclassification rate.

@@

\subsection*{Testing for statistical supervenience} % (fold)
\label{sub:subsection_name}

@@

The above theorem implies that if we desire to know whether a particular mental property is supervenient to a particular brain property, we must check whether $L^*=0$.  Unfortunately, $L^*$ is typically unknown.  Fortunately, we can approximate $L^*$ using training data.

Let $g_n$ be a classifier induced by the data, $g_n:\mB \times (\mc{M} \times \mc{B})^n \mapsto \mM$.   Assume that training data $\mc{T}_n=\{(M_{1},B_{1}), \ldots, (M_{n},B_{n})\}$ are each sampled identically and independently (iid) from the true (but unknown) joint distribution, $F_{MB}$.  The misclassification rate of such a classifier is given by:
\begin{align}
L_F(g_n)=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m],
\end{align}
%  The expected misclassification rate is given by 
% \begin{align}
% \EE[L_F(g_n)]=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m],
% \end{align}
% where the expectation is taken with respect 
Calculating the misclassification rate is often intractable in practice because it requires a sum over all possible mind/brain property pairs.  Instead, misclassification rate is approximated by ``hold-out'' error.  Let $\mc{H}_{n'}=\{(M_{n+1},B_{n+1}), \ldots, (M_{n+n'},B_{n+n'})\}$ be a set of $n'$ hold-out samples, each sampled iid from $F_{MB}$.  The hold-out approximation to misclassification rate is given by
\begin{align}
\hL^{n'}_{F}(g_{n}) = \sum_{(m,b) \in \mc{H}_{n'}}\II \{g_{n}(b; \mc{T}_{n})\neq m], % \PP[B=b,M=m].	
\end{align}
% Under the above assumptions, $\hL^{n'}_F(g_n)$ 
which can be used as a surrogate for $L^*$. 
By definition of $g^*$, the expectation of $\hL^{n'}_F(g_n)$ is greater than or equal to $g^*$ for any $g_n$ and all $n$.  Thus, we can construct a hypothesis test for $L^*$ using the surrogate $\hL^{n'}_F(g_n)$.

A statistical test proceeds by calculating a test statistic and a critical value $c_\alpha$.  We reject if the test statistic is more extreme than the critical value, or equivalently, if the $p$-value is less than $\alpha$.   The $p$-value, the probability of rejecting a true null hypothesis, is a functional of the distribution of the test statistic.

Ideally, we might consider the following hypothesis test: $H_0: L^*>0$ and $H_A: L^*=0$.  Unfortunately, because the null hypothesis is not closed, the alternate hypothesis lies on the boundary, so the $p$-value is always equal to unity \cite{Bickel2000}.  To proceed, therefore, we introduce a relaxed notion of supervenience:
\begin{defi}
\label{def2}
Given $\varepsilon > 0$, $\mM$ is said to $\varepsilon$-\textit{supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\MeB$, if and only if $L_{F}(g^*) < \varepsilon$.
\end{defi}
\noindent Given this relaxation, consider the problem of testing for $\eps$-supervenience:
\begin{align*}
	H_0^{\eps}: L^* \geq \eps \\
	H_A^{\eps}: L^* < \eps
\end{align*}
Let $\mh{n}= n' \hL^{n'}_{F}(g_n)$ be the test statistic.  The distribution of $\mh{n}$ is available under the least favorable distribution of the alternate hypothesis.  For the above hypothesis test,  the $p$-value is given by the binomial cumulative distribution function, $\mathbb{B}(\mh{n}; n', p_{H_A})= \sum_{k \in [\mh{n}]_0}$Binomial$(k; n'; p_{H_A})$, where $p_{H_A}$ is Bernoulli probability under least favorable distribution of the alternate hypothesis and $[\mh{n}]_0=\{0,1,\ldots, \mh{n}\}$.  In this composite alternate hypothesis, $p_{H_A}=\eps$.  We therefore reject whenever this $p$-value is less than $\alpha$; rejection implies that we are $100(1-\alpha$)\% confident that $\MeB$.   The definition of $\eps$-supervenience therefore admits, for the first time to our knowledge, a viable statistical test of supervenience, given a specified $\eps$ and $\alpha$.

% Because Binomial$(k; n', 0)=1$ for all $n'$, the $p$-value is always equal to unity.    Thus, we can \emph{never} reject the above null hypothesis, no matter how much data we obtain.

% Although the above theorem is of potential theoretical interest, the argument relies on knowing the typically unavailable $L^*$, rendering it useless pragmatically.  However,  $g^*$ could be estimated from data, and its estimate could be utilized to conduct the following statistical test of supervenience:
% % Let $g_n$ be a classifier induced from some training data, $\mc{T}_n$, 
% \begin{align*} 
% 	H_0:& L^* > 0 \\
% 	H_A:& L^*=0
% \end{align*}

% \subsection*{$\eps$-supervenience admits hypothesis testing} % (fold)
% \label{sub:hypothesis_testing}
% 
% We therefore consider a relaxed notion of supervenience:
% 
% 
% The $p$-value of the above composite alternate hypothesis is given by the binomial distribution under the least favorable distribution, $\mathbb{B}(\mh{n}; n', p_{H_A}=\eps)<1$.

\subsection*{The power and limits of an ideal test of supervenience} % (fold)
\label{sub:uc}

Ideally, as $n$ increases, the power of a test (the probability of a rejecting the null when it is false)  goes to unity. For any statistical test, if the $p$-value converges in distribution to $\delta_0$ (a point mass at zero), then whenever $\alpha >0$, power goes to unity.  For the above statistical test, if $g_n \conv g^*$ as $n \conv \infty$, then $L^{n'}_F(g_n) \conv L^*$ as $n' \conv \infty$.  Thus, if $L^* < \eps$, the $p$-value converges; that is, $\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n)) \conv \delta_0$.

% probability of both a Type I error (rejection of a true null hypothesis) and a Type II error (failure to reject a false null hypothesis) goes to zero.

@@

% The $p$-value 
% (probability of a type I error)
% of the test statistic for any classifier $g_n$ converges to zero, because $\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n))) \conv 0$ as $n,n' \conv \infty$. The power of the test (probability of not making a type II error), however, only converges to unity under certain conditions.  Specifically, let a  \emph{consistent} classifier be any classifier with expected misclassification rate converging to the Bayes optimal limit; that is, $\EE[L_{F}(g_n)] \conv L_{F}(g^*)$ as $n\conv \infty$. The power of the test can be written as: $\PP[\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n)) < \mathbb{B}(\mh{n}; n', \eps)]$.  As $n,n' \conv \infty$, $\mathbb{B}(\mh{n}; n', \hL^{n'}_F(g_n)) \conv \mathbb{B}(\mh{n}; n', L^*)$.  And if $L^* < \eps$, then $\mathbb{B}(\mh{n}; n', L^*) < \mathbb{B}(\mh{n}; n', \eps)$.  So, the probability of a Type II error also goes to zero as $n,n' \conv \infty$.

@@

The above considerations indicate that to obtain a statistical test with unity power, a consistent classifier (one for which $g_n \conv g^*$ as $n \conv \infty$) is required. Below, we show that under a very general mind-brain model, a consistent classifier is readily available.

@@

\begin{thex}
Let the physical property under consideration be brain connectivity structure, so $b$ is a brain-graph (``connectome'') with vertices representing neurons (or collections thereof) and edges representing synapses (or collections thereof). Further let $\mB$, the brain observation space, be the collection of all graphs on a finite number of vertices, and $\mc{M}$, the mental property observation space, be finite. Now, imagine collecting very large amounts of very accurate exchangeable  brain-graph data and the associated mental property indicators. A $k_n$-nearest neighbor classifier using an isomorphism-matching Frobenius norm is universally consistent (see Methods for details). Therefore, %Theorem \ref{thm1} applies and 
the existence of a universally consistent classifier guarantees that eventually (in $n,n'$) we will be able to conclude $\MeB$ for this mind-brain property pair, if indeed $\varepsilon$-supervenience holds. This logic holds for directed graphs or multigraphs or hypergraphs with discrete edge weights and vertex attributes. Furthermore, the proof holds for other matrix norms (which might speed up convergence), and the regression scenario, where $|\mM|$ is infinite (again, see Methods for details).  
\end{thex}

@@

We have introduced the notion of $\eps$-supervenience, which states that the Bayes optimal misclassification rate for any mind-brain property pair is less than $\eps$.  This definition admits, for the first time to our knowledge, a viable statistical test for supervenience.  Furthermore, when we restrict the space of minds and brains to the setting of \emph{Gedankenexperiment}  1, we have shown that $k_n$-NN classifiers are universally consistent, such that one can derive a hypothesis test, with confidence level $\alpha$, that is guaranteed to converge to the Bayes optimal misclassification rate, given sufficient data, no matter the true (but unknown) distribution of mind-brain pair properties.

@@

Thus, given measurement of mental and brain properties that we believe reflect the properties of interest, and a sufficient amount data satisfying the exchangeability assumption, a rejection of $H_0^\eps$ entails that we are $100(1-a)\%$ confident that the mental property under investigation does not $\eps$-supervene on the brain property under investigation.  Unfortunately, failure to reject is more ambiguous. $\eps-$supervenience tests can therefore be thought of as constraining the space of possible brain properties upon which a mental property supervenes.  Determining that a mental property does not supervene on \emph{any} brain property is beyond the capacities of this formalism.

Interestingly, much of contemporary research in neuroscience and cognitive science could be cast as mind-brain supervenience investigations.  Specifically, any investigation that aims to ``explain'' some behavioral or psychological phenomenon by reference to neural (or other brain) activity or structure, could be thought of as mind-brain supervenience investigations.  Thus, the proposed $\eps$-supervenience framework is perhaps a useful unifying perspective for these fields.  Perhaps this is especially true in light of the advent of ``connectomics'' \cite{SpornsKotter05,Hagmann05}, a field devoted to estimating whole organism brain-graphs, and relating them to function.  Testing supervenience of various mental properties on these brain-graphs will likely therefore become increasingly compelling; so the framework developed herein could be fundamental to these investigations.  
% Note that these connectomics investigations might lack any dynamics; rather, they effectively assume that structure determines the relevant dynamics.  Assuming that dynamics are a function of either vertex or edge attributes, whether any particular mental property is supervenient to ``only'' connectivity structure, or also some attributes, is merely another $\eps$-supervenience hypothesis. 
For example, questions about whether connectivity structure alone is sufficient to explain a particular mental property is one possible mind/brain $\eps$-supervenience investigation.  Appendix 2 presents an illustrative simulated example using the only currently known connectome---that of a Caenorhabditis elegans---demonstrating that $\eps$-supervenience can be rejected at some critical value $c_\alpha$ with only a reasonably small number of samples. Similar supervenience tests on larger animals will require either higher-throughput imaging modalities \cite{HayworthLichtman06, Bock2011} or more coarse brain-graphs \cite{PalmAmunts10,Johansen-Berg2009}, or both.

@@

% In conclusion, this \emph{Gedankenexperiment}, together with (i) the formal definition of $\varepsilon$-supervenience as a constraint on distributions, (ii) the brain-graph model, and (iii) the universal consistency proof on graphs, is the first demonstration (to our knowledge) that empirically investigating supervenience is at least theoretically possible. The above discussion suggests that many previously conducted investigations either assume supervenience, or try to test it.  Further, new technologies facilitate testing supervenience of mental properties on brain-graphs more easily.

\section*{Methods}
\label{sec:methods}

% Consider the following problem setup.  We have a collection of training data, $\mc{T}_n =\{(m_i,b_i)\}_{i=1}^n$, each sampled exchangeably from some unknown joint distribution, $(m_i,b_i)\sim F_{M,B}$, where $m_i$ and $b_i$ are the observed mental and brain properties of experiment $i$, respectively.  A new brain, $b$, called the ``test brain'', is then observed, and one desires to find the most likely class of the new brain, $m$.  It is further assumed that the test mind-brain pair is sampled from the same distribution as the training data, $(m,b)\sim F_{M,B}$, and $m$ is unobserved. Further assume that $m$ can take one of a finite number of possible values, that is, $|\mc{M}|<\infty$, and that  $\mc{B}$ is countable.

The $1$-nearest neighbor ($1$-NN) classifier works as follows.  Compute the distance between the test brain and all the training brains, $d_i=d(b,b_i)$ for all $i \in [n]$, where $[n]=1,2,\ldots, n$.  Then, sort them, $d_{(1)} < d_{(2)} < \ldots < d_{(n)}$, and their corresponding mental properties, , $m_{(1)}, m_{(2)}, \ldots, m_{(n)}$, where parenthetical indices indicate rank order.  %One can then also obtain a rank order for the training minds, $m_{(1)}, m_{(2)}, \ldots, m_{(n)}$, where $m_{(i)}$ is the class of the $i^{th}$ closest training brain to $b$.  
The $1$-NN algorithm predicts that the unobserved mind is of the same class as the closest brain's class: $\mh{m}=m_{(1)}$.  The $k_n$ nearest neighbor is a straightforward generalization of this approach.  It says that the test mind is in the same class as which ever class is the plurality class of the $k_n$ nearest neighbors, $\mh{m}=\argmax_{m'}\II\{\sum_{i=1}^{k_n} m_{(i)}=m'\}$.  Given a particular choice of $k_n$ (the number of nearest neighbors to consider), and a choice of $d(\cdot,\cdot)$ (the distance metric used to compare the test datum and training data), one then has a relatively simple and intuitive algorithm.

Let $g_n$ be the $k_n$ nearest neighbor ($k_n$NN) classifier when there are $n$ training samples.  
A collection of such classifiers $\{g_n\}$,  with $k_n$ increasing with $n$, is called a classifier sequence.  
A universally consistent classifier sequence is any classifier sequence that is guaranteed to converge to the Bayes optimal classifier regardless of the true distribution from which the data were sampled; that is, a universally consistent classifier sequence satisfies $g_n \conv g^*$ as $n \conv \infty$ for all $F_{MB}$.

% In particular, as $n$ increases, $k_n$ must also increase, but not quite as quickly.  Formally, $k_n$ must satisfy
The $k_n$NN classifier is consistent if (i) $k_n \conv \infty$ as $n \conv \infty$ and (ii) $k_n/n \conv 0$ as $n\conv\infty$ \cite{Stone1977}. In Stone's original proof \cite{Stone1977}, $b$ was assumed to be a $d$-dimensional vector, and the $L_2$ norm ($d(b,b')=\sum_{j=1}^d (b_j-b_j')^2$, where $j$ indexes elements of the $d$-dimensional vector) was shown to satisfy the constraints on a distance metric for this collection of classifiers to be universally consistent.  Later, others extended these results to apply to any $L_p$ norm \cite{DGL96}.  When brain-graphs are represented by their adjacency matrices, one can stack the columns of the adjacency matrices, effectively embedding graphs into a vector space, in which case Stone's theorem applies.  Stone's original proof also applied to the scenario when $|\mc{M}|$ was infinite, resulting in a universally consistent regression algorithm as well.

Note that the above extension of Stone's original theorem to the graph domain implicitly assumed that vertices were labeled, such that elements of the adjacency matrices could easily be compared across graphs.  In theory, when vertices are unlabeled, one could first map each graph to a quotient space invariant to isomorphisms, and then proceed as before.  Unfortunately, 
there is no known polynomial time complexity algorithm for graph isomorphism
% solving the graph-matching problem is currently NP-Incomplete (meaning it is not known to be either P or NP) 
\cite{GareyJohnson79}, so in practice, dealing with unlabeled vertices will likely be computationally challenging.

% \subsection*{Supervenience} % (fold)
% \label{sec:preliminaries}
